Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Details section): put_log2, put_log3, put_log4.

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log4](#func.get_log4) function described above.

>>>>

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log2](#func.get_log2) function described above.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log3](#func.get_log3) function described above.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log4](#func.get_log4) function described above.
